Fuzzy joins through deep learning

### 2018-07-30 paper2018/siamese_networks.tex
adding more
refer to figures in text

For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$, as shown in Figure~\ref{schroff_loss}.  For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
\begin{equation}
  l_{triple} =  \left[\|\bf{x_a} - \bf{x_p}\|^2 - \|\bf{x_a} -\bf{x_n}\|^2 + \alpha \right]_+
\label{schroff}
\end{equation}
where
\begin{equation}
 \left[.\right]_{+} = max(0, .)
\end{equation}
and the loss function that is minimized across all $N$ triples is given by
\begin{equation}
 L = \sum_{i}^{N} l_{triple}
\end{equation}
Note that in this formulation, it is assumed that embedding is normalized so $\|\bf{x} \| = 1$ because this normalization is robust across variations in illumination and contrast.  The value of $\alpha$ in the original work is a hyper-parameter that \cite{DBLP:conf/cvpr/SchroffKP15} was set to 0.2.

@@

 An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.  In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.

@@

Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.  Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.  Their loss function is an attempt to minimize this angle, as defined in the equation below.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}

@@

The inspiration for our loss is that triplet loss, in effect, only pushes the negative distance as far as $\alpha$; if the negative distance is larger than that, the total loss can become negative, which is then forced to 0.  However, the further the negative point is from the anchor, the better, so we want to push it as far away as possible, without a limit like $\alpha$.  To achieve this, we use hyperbolic tangent to compress all distances to the range 0 to 1, and substract the negative distance from 1.  Then our loss function simply needs to minimize both positive and negative numbers:

@@

>>>>

For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15}
propose a triplet loss function where the \textit{positive distances}
for each triplet $i$ in the set of $N$ triplets is separated from
\textit{negative distances} by a margin of $\alpha$, as shown in
Figure~\ref{schroff_loss} with the arrow pushing toward $\alpha$.  For
each of $N$ triples, $l_{triple}$ reflects the loss for a given triple
as follows: 
\begin{equation}
  l_{triple} =  \left[\|\bf{x_a} - \bf{x_p}\|^2 - \|\bf{x_a} -\bf{x_n}\|^2 + \alpha \right]_+
\label{schroff}
\end{equation}
where
\begin{equation}
 \left[.\right]_{+} = max(0, .)
\end{equation}
and the loss function that is minimized across all $N$ triples is given by
\begin{equation}
 L = \sum_{i}^{N} l_{triple}
\end{equation}
Note that in this formulation, it is assumed that embedding is normalized so $\|\bf{x} \| = 1$ because this normalization is robust across variations in illumination and contrast.  The value of $\alpha$ in the original work is a hyper-parameter that \cite{DBLP:conf/cvpr/SchroffKP15} was set to 0.2.

@@

 An improvement over the triplet loss function is proposed by
 \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in
 videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this
 function that we refer to as `improved loss' in the paper considers
 the distances from the \textit{positive} element of the triplet to
 the \textit{negative} element, and tries to push that
 difference toward $\alpha$ as well as the distance from
 \textit{anchor} to the \textit{negative}.  We show this in
 Figure~\ref{modified_loss} with two push arrows.  In addition, it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.

@@

Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel
angular loss function which is not based on pairwise distances, but
rather is based on the angles of the triangle formed by the
\textit{anchor}, \textit{positive} and the \textit{negative} triplet.
Conceptually, they point out that since the \textit{anchor} and the
\textit{positive} pairs belong to the same class, the angle formed by
the \textit{anchor}, \textit{negative}, and \textit{positive} elements
should be as small as possible within that triangle.  Their loss
function is an attempt to minimize this angle, as defined in the
equations below.  The rough idea is that moving the positive nearer
and the negative further away each reduce the angle, which we
illustrate in Figure~\ref{angular_loss} with the angle to shrink.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}

@@

The inspiration for our loss is that triplet loss, in effect, only
pushes the negative distance as far as $\alpha$; if the negative
distance is larger than that, the total loss can become negative,
which is then forced to 0.  However, the further the negative point is
from the anchor, the better, so we want to push it as far away as
possible, without a limit like $\alpha$.  This is illustrated in
Figure~\ref{tanh_loss} by pushing toward $\infty$.  To achieve this,
we use hyperbolic tangent to compress all distances to the range 0 to
1, and substract the negative distance from 1.  Then our loss function
simply needs to minimize both positive and negative numbers:

@@

\input{triplet_selection}
